Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
Add max planning time result

To calculate SMAPE for each $\alpha$,
we compute tuple-wise absolute percentage deviations within each iteration of each query, and
average this value over all iterations.
Relative errors of query results, when optimizing for quality
($\alpha=0$), are low --- between \lowsmapealphazero{} and
\highsmapealphazero{} --- indicating that on-the-fly imputation produces
results similar to the baseline. When optimizing for performance ($\alpha=1$),
relative errors can be modestly higher --- up to \highsmapealphaone{} in the
worst case, as this approach most closely corresponds to dropping all
\nullv{}s. Thus, it is important to recognize the tradeoffs between quality and
performance for the specific use case.

@@

Planning times for our benchmark queries are reasonable, with mean planning
times across the benchmark queries ranging from \planninglowtime{} ms to
\planninghightime{} ms, and ranging from \planninglowtimepct{} to
\planninghightimepct{} as a share of total runtime.  In all cases, the
optimizer returned a query plan within \planningmaxtime{} ms. The choice of
$\alpha$ has no impact on planning times, because query selection is done after
collecting the Pareto frontier.

>>>>

To calculate SMAPE for each $\alpha$,
we compute tuple-wise absolute percentage deviations within each iteration of each query, and
average this value over all iterations.
Relative errors of query results, when optimizing for quality
($\alpha=0$), are low --- between \lowsmapealphazero{} and
\highsmapealphazero{}\% --- indicating that on-the-fly imputation produces
results similar to the baseline. When optimizing for performance ($\alpha=1$),
relative errors can be modestly higher --- up to \highsmapealphaone{}\% in the
worst case, as this approach most closely corresponds to dropping all
\nullv{}s. Thus, it is important to recognize the tradeoffs between quality and
performance for a specific use case.

@@

Planning times for our benchmark queries are reasonable, with mean planning times across the
benchmark queries ranging from \planningtimelow{} to \planningtimehigh{}, and ranging from
\planningtimelowpct{} to \planningtimehighpct{}\% of total runtime. In 99\% of individual
cases, the optimizer returned a query plan with \planningtimepninetynine{}. The choice of
$\alpha$ has no impact on planning times, because query selection is done after collecting
the Pareto frontier.
